Adaptive Sequential Model Selection

### 2015-05-12 paper.tex
added theorem on L1 penalized exponential families

\section{Computation}

@@

As we see below, a similar result holds for the LASSO ever-active path. In fact, it holds for a much larger class of $\ell_1$ regularized exponential family models including the graphical LASSO, group LASSO, and...
\WFcomment{Fill in this proof.}

>>>>

\section{Computation}\label{sec:computation}

@@

As we see below, a similar result holds for the LASSO ever-active path. In fact, it holds for a much larger class of $\ell_1$ regularized exponential family models including the graphical LASSO, group LASSO, and... \WFcomment{more? group LASSO not really $\ell_1$ penalty, but the result is true for group LASSO}

\begin{theorem}
  Assume that $M_\infty$ is an exponential family model
  of the form
  \[
  Y \sim \exp\{ \theta'U(y) - \psi(\theta) \}\,d\nu(y),
  \]
  with $\Theta \sub \R^p$ convex, and assume
  that the model path $M_{[d]}$ is given 
  by the ever-active set for the $\ell_1$-penalized problem
  \begin{equation}\label{eq:regProblem}
  \hat\theta^r = \argmin_{\theta\in \Theta} 
  -\ell(\theta) + \lambda_r\|\theta\|_1,
  \end{equation}
  for some sequence $\lambda_r > 0$.

  Then, for a candidate active set $E$ of size $k$, 
  the set $A = \{E_k = E, \;U_E = u\}$ is characterized 
  exactly by the constraints $U_E = u$ and
  \[
  v_j^-(E,t) \leq U_j(Y) \leq v_j^+(E,t), \quad\forall j \notin E,
  \]
  for $v_j^-$ and $v_j^+$ given explicitly in
  Equations~(\ref{eq:vMinus_L1}--\ref{eq:vPlus_L1}).
  Thus, $A$ corresponds exactly to 
  a set with $2(p-k)$ linear inequality constraints and $k$
  linear equality constraints on $U(Y)$.
\end{theorem}

\begin{proof}
  Note that, because exponential family likelihoods are concave in their natural parameters, the problem in~\eqref{eq:regProblem} is convex. Again, once we know the sufficient statistics $U_E(Y)$ for model $k$, and that $E_k=E$, we know that
  \[
  \hat\theta^r = \hat\theta^{(E,r)}
  \]
  for every $r \leq R_k$, so we know the entire path of fits up to and including $R_k$. But then, excluding variable $j \notin E$ at Lagrange parameter $\lambda_r$ is equivalent to
  \[
  \lambda_r \geq 
  \left| \pardd{\ell(\hat\theta^r)}{\theta_j} \right|
  = \left|U_j - \E_{\hat\theta^r}[U_j]\right|
  \]
  On $A$, for $r \leq R_k$, 
  $\E_{\hat\theta^r}[U_j]$ is a known function of $E$ and $u$,
  so we can set
  \begin{align}\label{eq:vMinus_L1}
    v_j^-(E,u) &= \sup_{r \leq R_k} \;\; 
    \E_{\hat\theta^r}[U_j] - \lambda_r \\
    \label{eq:vPlus_L1}
    v_j^+(E,u) &= \inf_{r \leq R_k} \;\;
    \E_{\hat\theta^r}[U_j] + \lambda_r .
  \end{align}
\end{proof}
